\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2016-07-21 redaction/dhp_draft_july2016.tex
Petite modif dans la rédaction

\begin{eqnarray}
\tau_{ikt}&=&\exp\left(\sum_{i \neq \text{ARG}}\alpha_i.\mathbb{1}_i\right).\exp\left(\sum_k\beta_k.\mathbb{1}_k\right).\exp\left(\sum_{t \neq 1974}\gamma_t.\mathbb{1}_t\right) .\exp\left(\epsilon_{ikt}\right) \notag \\
\Leftrightarrow \ln(\tau_{ikt})&=&\sum_{i \neq \text{ARG}}\alpha_i.\mathbb{1}_i + \sum_k\beta_k.\mathbb{1}_k + \sum_{t \neq 1974}\gamma_t.\mathbb{1}_t+\epsilon_{ikt}
\end{eqnarray}

@@

Figure ???? reports the time effect as the $\Gamma_t$ in the iceberg and multiplicative case and as $100.\exp(\gamma_t)$ in the additive case (assuming $\gamma_{1974}=0$).

>>>>

\begin{eqnarray}
\tau_{ikt}&=&cst.\exp\left(\sum_{i \neq \text{AFG}}\alpha_i.\mathbb{1}_i\right).\exp\left(\sum_{k\neq \text{011}}\beta_k.\mathbb{1}_k\right).\exp\left(\sum_{t \neq 1974}\gamma_t.\mathbb{1}_t\right) .\exp\left(\epsilon_{ikt}\right) \notag \\
\Leftrightarrow \ln(\tau_{ikt})&=&cst+\sum_{i \neq \text{AFG}}\alpha_i.\mathbb{1}_i + \sum_{k\neq \text{011}}\beta_k.\mathbb{1}_k + \sum_{t \neq 1974}\gamma_t.\mathbb{1}_t+\epsilon_{ikt}
\end{eqnarray}

@@

Figure ???? reports the time effect as the $\Gamma_t$ in the iceberg and multiplicative case and as $100.\exp(\gamma_t)$ in the additive case (assuming in both cases that $\gamma_{1974}=0$).
